---
title: "Media Multitasking and Bilingualism: Initial Analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

This Rmd file contains code for an initial analysis of the experiment "Media Multitasking and Bilingualism." All data were collected in Fall 2018 at the University of California, Santa Barbara.

Contributors: Xinyang Miao, Jacob T. Fisher, Rene Weber

```{r setup, include=FALSE}
library(psych)
library(knitr)
library(tidyverse)
library(stringr)
library(purrr)
library(tidyr)
knitr::opts_chunk$set(echo = TRUE)
```

First, let's ingest the data. We have a list of csv files that contain the reaction time and accuracy data from the experiment, and we also have a large csv file that contains the survey data and post hoc memory task. We will ingest the files separately and then merge them later.

```{r}
# Commenting the below stuff out since we only need to combine everything together once.

# files = list.files(path ="data/exp_data", pattern="*.csv", full.names = TRUE)
#exp_data = do.call(plyr::rbind.fill, lapply(files, function(x) read.csv(x, as.is=TRUE, stringsAsFactors = FALSE)))

surveydata = read.csv("data/surveydata.csv", stringsAsFactors = FALSE,  dec = ".")
exp_data = read.csv("data/expdata.csv")
```

## TODO

- Create MMI and cross language MMI variables (Jacob will do this)
- Create bilingualism variable
- Code questions for each audiobook as a % correct variable
- Code enjoyment and attention scales for each audiobook
- Note participants who failed compliance check (create a new variable that is 1 if they answered "yes" to either of the compliance check questions and 0 otherwise)
- Remove outliers from matching task (RTs that were either way too fast or way too slow)
- Get % accuracy and RT measures for matching task during each audiobook
- Merge surveydata and exp_data

```{r}
exp_data <- rename(exp_data, RT = key_resp_1.rt, corr = key_resp_1.corr)

# Creating a variable that captures the book that they were listening to

exp_data <- mutate(exp_data, 
               cond = case_when(str_detect(sounds, "animalfarm_chinese") == TRUE ~ "animalfarm_chinese",
                                str_detect(sounds, "greatgatsby_english") == TRUE ~ "greatgatsby_english",
                                str_detect(sounds, "greatgatsby_chinese") == TRUE ~ "greatgatsby_chinese",
                                str_detect(sounds, "animalfarm_english") == TRUE ~ "animalfarm_english",
                                str_detect(sounds, "animalfarm_spanish") == TRUE ~ "animalfarm_spanish",
                                str_detect(sounds, "greatgatsby_spanish") == TRUE ~ "greatgatsby_spanish",
                                TRUE ~ NA_character_))

#Creating a variable that captures the language condition they were in
exp_data <- exp_data %>% 
  group_by(participant) %>% 
  mutate(lang = ifelse("animalfarm_spanish" %in% cond | "greatgatsby_spanish" %in% cond, "spanish", ifelse("animalfarm_chinese" %in% cond | "greatgatsby_chinese" %in% cond, "chinese", NA))) %>% ungroup()

#Creating a variable that captures the book they were listening to and the language the book was in separately
exp_data <- exp_data %>% separate(cond, into = c("booktitle", "booklang"), sep = "_", remove=FALSE)

# Creating a variable that captures whether this is the first or second book they've listened to

exp_data <- exp_data %>% mutate(trial = ifelse(trials_2.thisTrialN == 0, 1, 2))
```

# EDA 
First we're just going to do some EDA to get a sense of the experiment data. Here are a few things that I'm going to plot:

- Number of trials per condition (to make sure we don't have wildly more trials in one condition than another)
- Number of trials per participant (to check for outliers)
- Mean response time and correctness per subject
- Distribution of response times and correctness
- Mean response time and correctness per condition
- Mean response time and correctness per condition and per subject
- Mean response time and correctness per condition and per language (chinese or spanish)

```{r}
# Number of trials per condition
ggplot(exp_data, aes(x = as.factor(cond))) + 
  geom_bar(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90))

# Number of trials per participant (filtering NAs)
ggplot(filter(exp_data, !is.na(RT)), aes(x = as.factor(participant))) + 
  geom_bar(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90))

# Number of NA trials per participant
ggplot(filter(exp_data, is.na(RT)), aes(x = as.factor(participant))) + 
  geom_bar(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90))

```

Looks like there are a few that we should probably toss based on the number of NAs that they have. At least 1002 and likely 1007, 1029, 1041, 1063, and 1070  

```{r}

# Mean response time per subject
ggplot(exp_data, aes(x = as.factor(participant), y=RT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90))

#Distribution of response times
ggplot(exp_data, aes(x = RT)) + geom_histogram()
# Pretty left-skewed but that's to be expected in a task like this.

# Proportion correct per subject

ggplot(exp_data, aes(x = as.factor(participant), y=corr)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90))

```

Looks like pretty much everyone is correct most of the time which is good. We have a few who are correct much less often and it will be interesting to see how that relates to their language proficiency

```{r}

# correctness per word
ggplot(filter(exp_data, !is.na(corr)), aes(x = reorder(as.factor(name), corr), fill=(corrAns), y=corr)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90))

# RT per word
ggplot(filter(exp_data, !is.na(RT)), aes(x = reorder(as.factor(name), RT), fill=(corrAns), y=RT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90))

```

```{r}
# Correctness by trial (to see whether people gave up in the second trial)

ggplot(filter(exp_data, !is.na(corr)), aes(x = as.factor(trial), y=corr)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90)) + facet_wrap(~ lang)

# RT by trial (to see whether people gave up in the second trial)

ggplot(filter(exp_data, !is.na(RT)), aes(x = as.factor(trial), y=RT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90)) + facet_wrap(~ lang)

# Correctness by book

ggplot(filter(exp_data, !is.na(corr)), aes(x = as.factor(booklang), y=corr)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90)) + facet_wrap(~ booktitle)

# Correctness by book

ggplot(filter(exp_data, !is.na(RT)), aes(x = as.factor(booklang), y=RT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90)) + facet_wrap(~ booktitle)

```

Looks like people definitely responded faster in the second trial. It's good that we varied the order of presentation. There a re also some between book differences that are interesting, but I'm not sure what to make of them. I'll come back to this if I have time. 

```{r}

# Mean response time per condition

plt_data <- exp_data %>% group_by(participant, lang, cond) %>% summarize(meanRT = mean(RT, na.rm=TRUE), meancorr = mean(corr, na.rm = TRUE)) %>% ungroup() %>% mutate(cut = cut_number(participant, 7))

ggplot(plt_data, aes(x = as.factor(cond), fill = as.factor(cond), y=meanRT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90)) + facet_wrap(~ lang)

ggplot(plt_data, aes(x = as.factor(cond), fill = as.factor(cond), y=meancorr)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90)) + facet_wrap(~ lang)

ggplot(filter(plt_data, lang=="spanish"), aes(x = as.factor(participant), fill = as.factor(cond), y=meanRT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90))

ggplot(filter(plt_data, lang=="chinese"), aes(x = as.factor(participant), fill = as.factor(cond), y=meanRT)) + 
  geom_bar(stat ="summary", fun.y='mean', position='dodge') + 
  theme(axis.text.x = element_text(angle = 90))

```

Interesting! There are pretty robust differences between conditions for each subject, but themeans are not that different from one another. It seems that there is something that they are interacting with, but I'm not sure what yet. If it's language (as we hypothesized) then it will be pretty cool. There isn't much more I can do without incorporating the survey data so that's what I'm going to do now.

## Survey Data Preprocessing

```{r}

surveydata <- surveydata %>% slice(-c(1,2))

surveydata <- surveydata %>% 
  mutate_at(vars(starts_with("Q")), funs = is.character, as.numeric) %>%
  mutate(age = case_when(age == "" ~ NA_character_,
                         TRUE ~ age))

surveydata <- surveydata %>% rename(participant = Q1.1, 
                                    age = Q2.2,
                                    sex = Q2.3,
                                    eth = Q2.4)

surveydata <- surveydata %>% 
  mutate(polychron = rowMeans(select(., starts_with("Q3.1")), na.rm=TRUE))

```

Calculating the MMI

The equation is $\sum\limits_{i=1}^{1} \frac{m_i x h_i}{h_{total}}$. Where $m_i$ is the total amount of time that the person spent multitasking using that medium and $h_i$ is the total amount of time the person reported using the medium and $h_total$ is the total amount of time the participant reported using media during a typical week.

As a side note I think that one of the main reasons I want to come up with a new version of the MMI is because the MMI is just such as pain in the behind to do anything with. 

```{r}

media_use <- surveydata %>% select('participant', starts_with('Q4.'))
media_use <- media_use %>% mutate(total_media_use = rowSums(select(., starts_with("Q4")), na.rm=TRUE))

MMI <- surveydata %>% select('participant', starts_with('Q5.'))
MMI <- MMI %>% mutate_at(vars(starts_with("Q")), funs(recode(., "1" = 0, "2" = .33, "3" = .67, "4" = 1)))

MMI <- full_join(MMI,media_use, by="participant")

MMI <- MMI %>% rename(print_u = Q4.1_1,
                      tv_u = Q4.1_2,
                      comp_vid_u = Q4.1_3,
                      music_u = Q4.1_4,
                      nm_audio_u = Q4.1_5,
                      vgs_u = Q4.1_6, 
                      phone_u = Q4.1_7,
                      im_u = Q4.1_8,
                      txt_u  = Q4.1_9,
                      eml_u = Q4.1_10, 
                      web_u = Q4.1_11,
                      comp_apps_u = Q4.1_12,
                      mob_apps_u = Q4.1_13)

MMI <- MMI %>% mutate(
  MMI_weighted = rowSums(cbind(
    ((print_u * rowSums(select(MMI, matches("Q5\\.1_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((tv_u * rowSums(select(MMI, matches("Q5\\.2_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((comp_vid_u * rowSums(select(MMI, matches("Q5\\.3_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((music_u * rowSums(select(MMI, matches("Q5\\.4_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((nm_audio_u * rowSums(select(MMI, matches("Q5\\.5_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((vgs_u * rowSums(select(MMI, matches("Q5\\.6_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((phone_u * rowSums(select(MMI, matches("Q5\\.7_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((im_u * rowSums(select(MMI, matches("Q5\\.8_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((txt_u * rowSums(select(MMI, matches("Q5\\.9_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((eml_u * rowSums(select(MMI, matches("Q5\\.10_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((web_u * rowSums(select(MMI, matches("Q5\\.11_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((comp_apps_u * rowSums(select(MMI, matches("Q5\\.12_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use),
    ((mob_apps_u * rowSums(select(MMI, matches("Q5\\.13_[[:digit:]]{1}")), na.rm=TRUE))/total_media_use)
    ), na.rm=TRUE))

# This is the extra item that we asked regarding how often the person multitasks with media in a different language while using this primary medium. Since we only have one item, we don't need to take the rowsums within each category, just the sum across all media types.

MMI <- MMI %>% mutate(
  MMI_lang = rowSums(cbind(
    ((print_u * Q5.1.1)/total_media_use) * 4,
    ((tv_u * Q5.2.1)/total_media_use)* 4,
    ((comp_vid_u * Q5.3.1)/total_media_use)* 4,
    ((music_u * Q5.4.1)/total_media_use)* 4,
    ((nm_audio_u * Q5.5.1)/total_media_use)* 4,
    ((vgs_u * Q5.6.1)/total_media_use)* 4,
    ((phone_u * Q5.7.1)/total_media_use)* 4,
    ((im_u * Q5.8.1)/total_media_use)* 4,
    ((txt_u * Q5.9.1)/total_media_use)* 4,
    ((eml_u * Q5.10.1)/total_media_use)* 4,
    ((web_u * Q5.11.1)/total_media_use)* 4,
    ((comp_apps_u * Q5.12.1)/total_media_use)* 4,
    ((mob_apps_u * Q5.13.1)/total_media_use)* 4
    ), na.rm=TRUE))

MMI_s <- MMI %>% select(participant, MMI_weighted, MMI_lang)

surveydata <- full_join(surveydata, MMI_s, by="participant")

```

Okay now I have to calculate the bilingualism measures. This is going to be a huge pain too I think. The scale that we landed on adds points to one category or another based on a person's answers to each question. So we are going to need to create a variable that we can then iteratively add points to based on their answers to each of the bilingualism questions.  Scoring taken from [here](https://www.researchgate.net/publication/231841097_A_quick_gradient_Bilingual_Dominance_Scale). We left off the last item of hte scale because it was "In what country do you currently live?" Since everyone is living in America we went ahead and added +4 to the english variable, as would be the case if they answered any english speaking country in item 12.

```{r}

bilingualism <- surveydata %>% select(participant, starts_with("Q6"), -ends_with("b"))

bilingualism <- bilingualism %>% 
  mutate(other_lang = case_when(Q6.1 == 1 ~ "mandarin",
                                Q6.1 == 2 ~ "spanish",
                                TRUE ~ "other")) %>%
  mutate(tot_eng = 4, tot_other = 0) %>%
  mutate(tot_eng = case_when(Q6.2 == 1 ~ tot_eng + 5, #question 1 & 2 (6.2 and 6.4a from Qualtrics)
                        Q6.2 == 2 ~ tot_eng + 3,
                        Q6.2 == 3 ~ tot_eng + 1,
                        Q6.2 == 4 ~ tot_eng),
         tot_other = case_when(Q6.4a == 1 ~ tot_other + 5,
                        Q6.4a == 2 ~ tot_other + 3,
                        Q6.4a == 3 ~ tot_other + 1,
                        Q6.4a >= 4 ~ tot_other)) %>% 
  mutate(tot_eng = case_when(Q6.3 == 1 ~ tot_eng + 5, #question 3 & 4 (6.3 and 6.5a from Qualtrics)
                        Q6.3 == 2 ~ tot_eng + 3,
                        Q6.3 == 3 ~ tot_eng + 1,
                        Q6.3 >= 4 ~ tot_eng),
         tot_other = case_when(Q6.5a == 1 ~ tot_other + 5,
                        Q6.5a == 2 ~ tot_other + 3,
                        Q6.5a == 3 ~ tot_other + 1,
                        Q6.5a >= 4 ~ tot_other)) %>%
  mutate(tot_eng = case_when(Q6.6a == 1 ~ tot_eng + 5, #question 5 (6.6a from Qualtrics)
                        Q6.6a == 2 ~ tot_eng,
                        Q6.6a == 3 ~ tot_eng + 3),
         tot_other = case_when(Q6.6a == 1 ~ tot_other,
                        Q6.6a == 2 ~ tot_other + 5,
                        Q6.6a == 3 ~ tot_other + 3))  %>%
  mutate(tot_eng = case_when(Q6.7a == 1 ~ tot_eng + 5, #question 6 (6.7a from Qualtrics)
                        Q6.7a == 2 ~ tot_eng,
                        Q6.7a == 3 ~ tot_eng + 3,
                        TRUE ~ tot_eng),
         tot_other = case_when(Q6.7a == 1 ~ tot_other,
                        Q6.7a == 2 ~ tot_other + 5,
                        Q6.7a == 3 ~ tot_other + 3,
                        TRUE ~ tot_other)) %>%
  mutate(tot_eng = case_when(Q6.8a == 1 ~ tot_eng + 5, #question 7 (6.8a from Qualtrics)
                        Q6.8a == 2 ~ tot_eng,
                        Q6.8a == 3 ~ tot_eng + 3,
                        TRUE ~ tot_eng),
         tot_other = case_when(Q6.8a == 1 ~ tot_other,
                        Q6.8a == 2 ~ tot_other + 5,
                        Q6.8a == 3 ~ tot_other + 3,
                        TRUE ~ tot_other)) %>% 
  mutate(tot_eng = case_when(Q6.9a == 1 ~ tot_eng + 2, #question 8 (6.9a from Qualtrics)
                        Q6.9a == 2 ~ tot_eng),
         tot_other = case_when(Q6.9a == 1 ~ tot_other,
                        Q6.9a == 2 ~ tot_other + 2)) %>%
  mutate(tot_eng = case_when(Q6.10 == 1 ~ tot_eng + 1, #question 9 and 10 (6.10 and 6.11a from Qualtrics)
                        Q6.10 == 2 ~ tot_eng + 2),
         tot_other = case_when(Q6.11a == 1 ~ tot_other + 1,
                        Q6.11a == 2 ~ tot_other + 2)) %>% 
      mutate(tot_eng = case_when(Q6.12 == 1 & Q6.13a == 1 ~ tot_eng - 3, #question 11 (6.12 and 6.13a from Qualtrics)
                        TRUE ~ tot_eng),
         tot_other = case_when(Q6.12 == 1 & Q6.13a == 2 ~ tot_other - 3,
                        TRUE ~ tot_other)) %>% 
  mutate(dominance = tot_eng - tot_other) # will be positive for english dominance, negative for other dominance

bilingualism_s <- bilingualism %>% select(participant, tot_eng, tot_other, other_lang, dominance)
  
```

I can't help myself so I'm going to do a histogram.

```{r}
ggplot(bilingualism_s) + geom_histogram(aes(x = dominance, fill = other_lang), binwidth = 4)
```

I'm also going to do a big plot of the relationships between different types of media multitasking and bilingual dominance. 

```{r}
library(ggthemes)
MMI_lang_qs <- MMI %>% select(participant, ends_with(".1"))
MMI_lang_qs <- MMI_lang_qs %>% mutate_at(vars(starts_with("Q")), funs(recode(., "0" = 1, ".33" = 2, ".67" = 3, "1" = 4)))
MMI_lang_qs <- left_join(MMI_lang_qs, bilingualism_s, by="participant")
MMI_lang_qs <- MMI_lang_qs %>% rename("print" = "Q5.1.1",
                                      "tv" = "Q5.2.1",
                                      "computer_video" = "Q5.3.1",
                                      "music" = "Q5.4.1",
                                      "non_music_audio" = "Q5.5.1",
                                      "video_games" = "Q5.6.1",
                                      "phone-calls" = "Q5.7.1",
                                      "instant_messaging" = "Q5.8.1",
                                      "texting" = "Q5.9.1",
                                      "email" = "Q5.10.1",
                                      "web_surfing" = "Q5.11.1",
                                      "other_comp_apps" = "Q5.12.1",
                                      "other_mobile_apps" = "Q5.13.1")

MMI_lang_qs <- tidyr::pivot_longer(MMI_lang_qs, cols = print:other_mobile_apps, names_to = "media", values_to = "response", values_drop_na = TRUE)

ggplot(filter(MMI_lang_qs, media != "non_music_audio"), aes(x = dominance, y = response, color = media)) + geom_point() + geom_smooth(method = "lm") + facet_wrap(~ media) + theme_few()
```

Looks like our two groups are not equivalently bilingual, which is probably an issue. We will need to keep this in mind if we glom the two groups together.

Now adding in the correct answers to the cued recall questions

```{r}

question <- c('Q7.1', 'Q7.2', 'Q7.3', 'Q7.4', 'Q7.5', 'Q7.6', 'Q7.7', 'Q7.8',  'Q7.9', 'Q7.10', 'Q8.1', 'Q8.2', 'Q8.3', 'Q8.4', 'Q8.5', 'Q8.6', 'Q8.7', 'Q8.8',  'Q8.9', 'Q8.10')
answer <- c(1,3,2,3,1,2,4,1,3,3,2,1,2,3,1,4,1,3,1,2)

qa_correct <- data.frame(question, answer)

responses <- surveydata %>% select(participant, starts_with("Q7"), starts_with("Q8"))

responses <- responses %>% 
  group_by(participant) %>% 
  gather("question", "response", starts_with("Q"))

merged_answers <- responses %>% split(.$participant) %>%
  map(~ left_join(., qa_correct, by = "question")) %>% 
  map(~ mutate(., q_corr = ifelse(response - answer == 0, 1, 0))) %>%
  map_df(., bind_rows)

merged_answers <- filter(merged_answers, !is.na(participant) & participant > 1000)

scores <- merged_answers %>% 
  mutate(booktitle = case_when(str_detect(question, "Q7") == TRUE ~ 'animalfarm',
                          str_detect(question, "Q8") == TRUE ~ 'greatgatsby',
                          TRUE ~ NA_character_)) %>% 
  group_by(participant, booktitle) %>% 
  summarize(score = mean(q_corr))
```

Here are the the self-reported difficulty and enjoyment measures. 

English Audiobook

- Q10.1_1 - Matching difficulty
- Q10.1_2 - Attention to matching
- Q10.1_3 - Matching task enjoyment
- Q10.1_4 - Audiobook difficulty
- Q10.1_5 - Attention to audiobook
- Q10.1_6 - Audiobook enjoyment

Non-English Audiobook

- Q103_1 - Matching difficulty
- Q103_2 - Attention to matching
- Q103_3 - Matching task enjoyment
- Q103_4 - Audiobook difficulty
- Q103_5 - Attention to audiobook
- Q103_6 - Audiobook enjoyment

In order to get these to where I can plot them, I have to get them into long form. 

```{r}
self_reports <- surveydata %>% select(participant, starts_with("Q10.1"), starts_with("Q103"))

self_reports <- self_reports %>% rename('match-diff_eng' = Q10.1_1,
                                        'match-att_eng' = Q10.1_2,
                                        'match-enj_eng' = Q10.1_3,
                                        'book-diff_eng' = Q10.1_4,
                                        'book-att_eng' = Q10.1_5,
                                        'book-enj_eng' = Q10.1_6,
                                        'match-diff_oth' = Q103_1,
                                        'match-att_oth' = Q103_2,
                                        'match-enj_oth' = Q103_3,
                                        'book-diff_oth' = Q103_4,
                                        'book-att_oth' = Q103_5,
                                        'book-enj_oth' = Q103_6) %>%
  gather("question", "response", -participant) %>%
  separate(question, c('question', 'condition'), sep = "_") %>%
  filter(participant > 1000)

eng_responses <- self_reports %>% filter(condition == "eng")
oth_responses <- self_reports %>% filter(condition == "oth")

test1 <- eng_responses %>% 
  tidyr::pivot_wider(names_from = question,
              values_from = response)

test2 <- oth_responses %>% 
  tidyr::pivot_wider(names_from = question,
              values_from = response)

responses <- bind_rows(test1, test2)

```

Okay **finally** I am going to merge the surveydata with the exp_data in order to start working on the full analyses that I'm going to do for the ICA presentation. 

```{r}

polychronicity <- surveydata %>% select(participant, polychron)

surveydata_s <- left_join(MMI_s, bilingualism_s, by = "participant")
surveydata_s <- left_join(surveydata_s, polychronicity, by = "participant")
surveydata_s <- left_join(surveydata_s, scores, by = "participant")

expdata_f <- exp_data %>% 
  mutate(condition = case_when(booklang == "chinese" | booklang == "spanish" ~ "oth",
                              booklang == "english" ~ "eng",
                              TRUE ~ NA_character_),
         match = recode(corrAns, "x" = "non-match", "z" = "match"))

expdata_s <- exp_data %>% 
  group_by(participant, booktitle, corrAns) %>% 
  summarize(meanRT = psych::harmonic.mean(RT, na.rm = TRUE),
            sdRT = sd(RT, na.rm=TRUE),
            meancorr = mean(corr, na.rm = TRUE),
            booklang = first(booklang),
            trial = first(trial)) %>%
  filter(!is.na(booktitle)) %>%
  mutate(condition = case_when(booklang == "chinese" | booklang == "spanish" ~ "oth",
                              booklang == "english" ~ "eng",
                              TRUE ~ NA_character_),
         match = recode(corrAns, "x" = "non-match", "z" = "match")) %>%
  filter(!is.na(meanRT))

expdata_s$participant <- as.character(expdata_s$participant)
expdata_f$participant <- as.character(expdata_f$participant)

fulldata_s <- left_join(expdata_s, surveydata_s, by=c("participant", "booktitle"))
fulldata_f <- left_join(expdata_f, surveydata_s, by=c("participant", "booktitle"))

fulldata_s <- left_join(fulldata_s, responses, by = c("participant", "condition"))


fulldata_s <- fulldata_s %>% 
  pivot_longer('match-diff':'book-enj',
               names_to = "question", 
               values_to = "response"
               ) %>%
  filter(participant != 1002,
         participant != 1019,
         participant != 1041,
         participant != 1055,
         other_lang != "other")
```

Doing some plots

```{r}

ggplot(fulldata_s) + 
  geom_bar(aes(x = condition, fill = condition, y = meanRT), stat ="summary", fun.y='mean', position='dodge', width = 0.5) + 
  theme_few() + 
  theme(axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  scale_fill_few()

```

```{r}

plt_data <- fulldata_s %>% 
  mutate(lang_groups = case_when(dominance <= -1 ~ "Mostly Non-English",
                                 dominance > -1 & dominance < 9 ~ "Mid",
                                 dominance >= 9 ~ "Mostly English"),
         condition = case_when(condition == "eng" ~ "English",
                               condition == "oth" ~ "Non-English"),
         MMI_group = case_when(MMI_weighted <= 3.56 ~ "lo",
                               MMI_weighted > 3.56 & MMI_weighted < 4.87 ~ "mid",
                               MMI_weighted >= 4.87 ~ "hi"),
         MMI_lang_groups = case_when(MMI_lang <= 1.45 ~ "lo",
                                 MMI_lang > 1.45 & MMI_weighted < 2.38 ~ "mid",
                                 MMI_lang >= 2.44 ~ "hi"),
         meanRT = meanRT * 1000) %>% 
  group_by(condition, MMI_group) %>% 
  summarize(meanrt = mean(meanRT, na.rm=TRUE), 
            sert = plotrix::std.error(meanRT, na.rm = TRUE),
            meanscore = mean(score, na.rm = TRUE), 
            sescore = plotrix::std.error(score, na.rm = TRUE), 
            secorr = plotrix::std.error(meancorr, na.rm = TRUE),
            meancorr = mean(meancorr, na.rm = TRUE)) %>% 
  filter(MMI_group != "mid")

ggplot(plt_data) + 
  geom_point(aes(x = condition, color = MMI_group, y = meanscore)) + 
  geom_line(aes(x = condition, y = meanscore, color = MMI_group, group = MMI_group)) +
  geom_errorbar(aes(x=condition, ymin=meanscore-sescore, ymax=meanscore+sescore), width = 0.05) +
  # facet_wrap(~ lang_groups) +
  theme_few() +
  theme(axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  scale_color_few(name = "MMI Group", labels = c("High", "Low")) +
  labs(x = "Condition", y = "Recall Score")

ggplot(plt_data) + 
  geom_point(aes(x = condition, color = MMI_group, y = meanrt)) + 
  geom_line(aes(x = condition, y = meanrt, color = MMI_group, group = MMI_group)) +
  geom_errorbar(aes(x=condition, ymin=meanrt-sert, ymax=meanrt+sert), width = 0.05) +
  theme_few() +
  theme(axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  scale_color_few(name = "MMI Group", labels = c("High", "Low")) +
  labs(x = "Condition", y = "Mean Reaction Time (ms)")

ggplot(plt_data) + 
  geom_point(aes(x = condition, color = MMI_group, y = meancorr)) + 
  geom_line(aes(x = condition, y = meancorr, color = MMI_group, group = MMI_group)) +
  geom_errorbar(aes(x=condition, ymin=meancorr-secorr, ymax=meancorr+secorr), width = 0.05) +
  theme_few() +
  theme(axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  scale_color_few(name = "MMI Group", labels = c("High", "Low")) +
  labs(x = "Condition", y = "Percent Correct Matches")

```

```{r}

plt_data <- fulldata_s %>%
  group_by(participant) %>%
  mutate(lang_groups = case_when(dominance <= -10 ~ "hi_nat",
                                 dominance > -10 & dominance < 10 ~ "mid",
                                 dominance >= 10 ~ "hi_eng")) %>% 
  summarize(meanRT = mean(meanRT, na.rm=TRUE),
            dominance = first(dominance),
            meancorr = mean(meancorr, na.rm=TRUE),
            MMI_lang = mean(MMI_lang),
            score = mean(score))

ggplot(plt_data, aes(x = MMI_lang, y = score)) + 
  geom_point() +
  geom_jitter(color = "#c7c7c7") +
  geom_smooth(method = "lm", color = "#65a5d9") + 
  theme_few() +
  theme(axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  labs(x = "Cross-Language Multitasking", y = "Cued Recall Rcore")

# plotting correctness by book language, bilingualism, and primary second language

plt_data <- fulldata_s %>% 
  mutate(booklang = recode(booklang, "chinese" = "Mandarin-Language Book", 
                           "spanish" = "Spanish-Language Book",
                           "english" = "English-Language Book"))

plt1 <- ggplot(filter(plt_data, other_lang == "mandarin"), aes(x = dominance, y = score)) + 
  geom_point(color = "#c7c7c7") + 
  geom_smooth(method = "lm", color = "#65a5d9") + 
  facet_wrap(~ booklang) + 
  theme_few(base_size=13) +
  theme(text = element_text(family = "Arial"),
        axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  xlim(-22, 22) +
  labs(x = "Bilingualism", y = "Cued recall score", title = "Mandarin-Speaking Participants")

plt2 <- ggplot(filter(plt_data, other_lang == "spanish"), aes(x = dominance, y = score)) + 
  geom_point(color = "#c7c7c7") + 
  geom_smooth(method = "lm", color = "#65a5d9") + 
  facet_wrap(~ booklang) +
  theme_few(base_size=13) +
  theme(text = element_text(family = "Arial"),
        axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  xlim(-22, 22) +
  labs(x = "Bilingualism", y = "Cued recall score", title = "Spanish-Speaking Participants")

gridExtra::grid.arrange(plt1, plt2, nrow =2)

ggplot(plt_data, aes(x = dominance, y = score)) + 
  geom_point() + 
  geom_smooth(method = "lm", color = "#65a5d9") + 
  facet_wrap(~ booklang) +
  theme_few(base_size=13) +
  theme(text = element_text(family = "Arial"),
        axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  xlim(-22, 22) +
  labs(x = "Bilingualism", y = "Cued recall score")

# plotting self reported responses by second language, bilingualism (dominance), and book language 
plt_data <- fulldata_s %>% 
  #filter(str_detect(question, "-att") == TRUE) %>% 
  mutate(question = recode(question, "book-att" = "Attention to Book", 
                           "match-att" = "Attention to Matching Task",
                           "book-diff" = "Difficulty of Book",
                           "match-diff" = "Difficulty of Matching Task",
                           "book-enj" = "Enjoyment of Book",
                           "match-enj" = "Enjoyment of Matching Task")) %>%
  group_by(participant, question, condition) %>%
  summarize(response = mean(response, na.rm=TRUE), dominance = mean(dominance, na.rm = TRUE), MMI_lang = mean(MMI_lang, na.rm=TRUE))

plt1 <- ggplot(filter(plt_data, str_detect(question, "Attention") == TRUE), aes(x = MMI_lang, y = response, color = condition)) +  
  #geom_point() + 
  #geom_jitter() +
  geom_smooth(method = "lm", se=FALSE) + 
  ylim(1, 5) +
  facet_wrap(~ question) + 
  theme_few() + 
  theme(plot.margin = unit(c(20, 20, 20, 20), "pt")) +
  scale_color_few(name = "Condition", labels = c("English", "Non-English")) +
  labs(x = "Cross-language Multitasking", y = "Response", title = "Self-Reported Attention")

plt2 <- ggplot(filter(plt_data, str_detect(question, "Enjoyment") == TRUE), aes(x = MMI_lang, y = response, color = condition)) +  
  #geom_point() + 
  geom_smooth(method = "lm", se=FALSE) + 
  ylim(1, 5) +
  facet_wrap(~ question) + 
  theme_few() + 
  theme(plot.margin = unit(c(20, 20, 20, 20), "pt")) +
  scale_color_few(name = "Condition", labels = c("English", "Non-English")) +
  labs(x = "Cross-language Multitasking", y = "Response", title = "Self-Reported Enjoyment")

plt3 <- ggplot(filter(plt_data, str_detect(question, "Difficulty") == TRUE), aes(x = MMI_lang, y = response, color = condition)) +  
  #geom_point() + 
  geom_smooth(method = "lm", se=FALSE) +
  ylim(1, 5) +
  facet_wrap(~ question) + 
  theme_few() + 
  theme(plot.margin = unit(c(20, 20, 20, 20), "pt")) +
  scale_color_few(name = "Condition", labels = c("English", "Non-English")) +
  labs(x = "Cross-language Multitasking", y = "Response", title = "Self-Reported Difficulty")

gridExtra::grid.arrange(plt1, plt2, plt3, nrow =3)

plt_data <- fulldata_s %>% 
  mutate(condition = recode(condition, "oth" = "Non-English", 
                           "eng" = "English"))

ggplot(plt_data, aes(x = dominance, y = score, color = as.factor(other_lang))) +  
  geom_point() + 
  geom_smooth(method = "lm", se=TRUE) + 
  facet_wrap(~ condition) + 
  theme_few() + 
  theme(axis.title.y = element_text(margin = margin(8,8,8,8)),
        axis.title.x = element_text(margin = margin(8,8,8,8))) +
  scale_color_few(name = "Other Language") +
  labs(x = "Bilingualism", y = "Cued-Recall Score")

```

Now I need to look at the relationship between multitasking and cross-language multitasking. 

```{r}

plt_data <- fulldata_s %>%
  group_by(participant) %>%
  mutate(MMI_groups = case_when(MMI_weighted <= 3.56 ~ "lo",
                                 MMI_weighted > 3.56 & MMI_weighted < 4.87 ~ "mid",
                                 MMI_weighted >= 4.87 ~ "hi"),
         MMI_lang_groups = case_when(MMI_lang <= 1.45 ~ "lo",
                                 MMI_lang > 1.45 & MMI_weighted < 2.38 ~ "mid",
                                 MMI_lang >= 2.44 ~ "hi")) 

ggplot(filter(plt_data, other_lang != "other"), aes(x = dominance, y = MMI_weighted)) +
  geom_point(color = "#c7c7c7") + 
  geom_smooth(method = "lm", color = "#65a5d9") + 
  theme_few() + 
  labs(x = "Media Multitasking Index", y = "Cross-Langage Multitasking")

df <- fulldata_s %>% 
  group_by(participant, condition) %>% 
  summarize(meanRT = mean(meanRT, na.rm=TRUE),
            MMI_weighted = first(MMI_weighted),
            MMI_lang = first(MMI_lang), 
            dominance = first(dominance))

anova(lm(score ~ MMI_weighted*MMI_lang*condition, data=df))

```

Interestingly enough, we get a significant (negative) effect of MMI_lang after we account for the variance from MMI_weighted. Let's do a post-hoc t-test to look at it more. 

```{r}
df <- fulldata_s %>%
  group_by(participant) %>%
  mutate(MMI_groups = case_when(MMI_weighted <= 3.56 ~ "lo",
                                 MMI_weighted > 3.56 & MMI_weighted < 4.87 ~ "mid",
                                 MMI_weighted >= 4.87 ~ "hi"),
         MMI_lang_groups = case_when(MMI_lang <= 1.45 ~ "lo",
                                 MMI_lang > 1.45 & MMI_lang < 2.38 ~ "mid",
                                 MMI_lang >= 2.38 ~ "hi"))

df <- df %>% group_by(MMI_groups, MMI_lang_groups, participant, condition) %>% summarize(mem = mean(score, na.rm=TRUE)) %>% ungroup() %>% group_by(MMI_groups, MMI_lang_groups, condition) %>% summarize(se_mem = plotrix::std.error(mem), mem = mean(mem)) 

ggplot(data = df, aes(x = as.factor(condition), y = mem, color = as.factor(MMI_lang_groups), group = as.factor(MMI_lang_groups))) + 
  geom_point() +
  geom_line() +
  geom_errorbar(aes(x=as.factor(condition), ymin=mem-se_mem, ymax=mem+se_mem), width = 0.05) +
  # scale_x_discrete(limits = c("low", "high")) +
  theme(plot.margin = unit(c(6, 12, 6, 6), "pt")) +
  facet_wrap(~ MMI_groups)
  # scale_color_few(name = "Reward", labels = c("High", "Low")) +
  # labs(x = "Cognitive Load", y = "Secondary Task Reaction Time")

```

Now let's do some modeling.

```{r}

# First, let's do MMI * Condition on reactions in the primary task

jtools::plot_summs(lme4::lmer(RT ~ MMI_weighted*condition*dominance + (1|participant) + (1|participant:condition), data = fulldata_f))

jtools::summ(lme4::lmer(RT ~ MMI_weighted*condition*dominance + (1|participant) + (1|participant:condition), data = fulldata_f)) 

# Now, let's do MMI * Condition on correctness in the primary task (matching). Since each response is just a 1 or a 0. I need to do some grouping for this one to make sure the data are at the correct level (one observation per participant per condition)

df <- fulldata_f %>% 
  group_by(participant, condition) %>%
  mutate(MMI_groups = case_when(MMI_weighted <= 3.56 ~ 1,
                                 MMI_weighted > 3.56 & MMI_weighted < 4.87 ~ 0,
                                 MMI_weighted >= 4.87 ~ 2)) %>%
  summarize(corr = mean(corr, na.rm=TRUE),
            MMI_weighted = first(MMI_weighted),
            MMI_groups = first(MMI_groups),
            dominance = first(dominance)) %>%
  filter(!is.na(condition) & MMI_groups != 0)

jtools::plot_summs(lme4::lmer(corr ~ MMI_weighted*condition*dominance + (1|participant), data = df))

jtools::summ(lme4::lmer(corr ~ MMI_weighted*condition*dominance + (1|participant), data = df)) 

# Now, let's do MMI * Condition on correctness in the secondary task (memory recall). 

df <- fulldata_f %>% 
  group_by(participant, condition) %>%
  mutate(MMI_groups = case_when(MMI_weighted <= 3.56 ~ 1,
                                 MMI_weighted > 3.56 & MMI_weighted < 4.87 ~ 0,
                                 MMI_weighted >= 4.87 ~ 2)) %>%
  summarize(score = mean(score, na.rm=TRUE),
            MMI_weighted = first(MMI_weighted),
            MMI_groups = first(MMI_groups),
            dominance = first(dominance)) %>%
  filter(!is.na(condition) & MMI_groups != 0)

jtools::plot_summs(lme4::lmer(score ~ MMI_groups*condition*dominance + (1|participant), data = df))

jtools::summ(lme4::lmer(score ~ MMI_groups*condition*dominance + (1|participant), data = df)) 

```

Demo variables

```{r}
table(as.numeric(surveydata$sex, na.rm=TRUE))
mean(as.numeric(surveydata$age), na.rm=TRUE)
```

